A family of accessibility measures derived from spatial interaction principles

### 2025-10-22 paper_plos/paper_plos_V3.tex
V3 final edits AS

\linenumbers
\section{Introduction}\label{introduction}

@@

In summary, this paper makes two contributions: (1) we review how
spatial interaction modeling and accessibility share similar origins but
have diverged in focus and interpretation. (2) we introduce a family of
accessibility measures grounded in spatial interaction principles,
including total, singly, and doubly constrained cases and variants of
``accessible opportunities'' and ``accessible population''. These cases
and variants align with common measures such as Hansen-type
accessibility \citep{hansen1959}, competitive accessibility measures
such as the 2SFCA method \citep{shen1998, luo2003}, and market potential
models
\citep{harris_market_1954, vickermanAccessibilityAttractionPotential1974}.

@@

The remainder of this paper proceeds as follows. Sections 2-4 trace the
historical development of spatial interaction and accessibility
research, beginning with Newtonian gravitational analogies and
\citet{careyPrinciplesSocialScience1858} (Section 2), moving through
early researchers like \citet{ravensteinLawsMigration1885} to
\citet{stewartDemographicGravitationEvidence1948} who theorised and
formalized spatial interaction patterns (Section 3), and examining how
the ``gravity-based'' accessibility approach in \citet{hansen1959}
became the dominant approach in planning practice (Section 4). Section 5
presents the entropy-based family of spatial interaction models in
\citet{wilson1971}, explaining how the introduction of ``constraints''
(based on top-down known information as part of entropy-maximisation)
produce interpretable, unit-consistent flow estimates. Section 6
explores why accessibility and spatial interaction literature diverged
into separate branches despite their shared conceptual foundations.
Section 7 constitutes the paper's core contribution: we derive a family
of accessibility measures corresponding to different constraints applied
-- unconstrained, singly constrained, and doubly constrained cases --
demonstrating how each yields zone-level accessibility values expressed
in meaningful units (opportunities or population) rather than
unit-inconsistent indices. We illustrate each measure with numerical
examples that clarify the practical implications of different constraint
assumptions. Section 8 concludes by discussing how these constrained
measures can inform planning decisions and improve clarity in
accessibility analysis.

@@

\section{Newtonian's roots of human spatial interaction
research}\label{newtonians-roots-of-human-spatial-interaction-research}

@@

\section{Early research on human spatial interaction: from Ravenstein
(1885) to Stewart
(1948)}\label{early-research-on-human-spatial-interaction-from-ravenstein-1885-to-stewart-1948}

@@

\section{Hansen's gravity-based accessibility to
today}\label{grav-to-today}

@@

\section{Wilson's family of spatial interaction
models}\label{wilsons-family-of-spatial-interaction-models}

@@

Wilson's work is notable for many reasons. Rather than relying on a
universal constant like \(G\) or a scaling factor to balance units,
Wilson's models calibrate interaction flows through known empirical
constraints using principles of entropy maximisation. This results in
interpretable, balanced (given the system knowns are expressed in the
constraints), and unit-consistent \(ij\) flows. The balancing factors
themselves have been subject to various interpretations -- as terminal
costs \citep{dieter1962distribution}, weighted mean values
\citep{kirbyNormalizingFactorsGravity1970}, or as accessibility measures
themselves \citep{cesario1977new} (as suggested in \citet{Wilson1971})
and as rents \citep{morphetGravityModelCalibration2023} -- reflecting
ongoing efforts to understand what these mathematical constructs
represent behaviourally. In this way, the spatial interaction modeling
tradition can be seen to have succeeded where accessibility modeling
stalled. While Wilson's model produces results that are in units of flow
tethered to the system of analysis, which facilitates such
interpretations, Hansen-type measures (still widely used today in
accessibility work) yield outputs that reflect proportional -- not equal
-- relationships and typically lack interpretable units.

@@

\section{Accessibility and spatial interaction modelling: two divergent
research
streams}\label{accessibility-and-spatial-interaction-modelling-two-divergent-research-streams}

@@

\section{A family of accessibility measures: from proportionality to
equality}\label{a-family-of-accessibility-measures-from-proportionality-to-equality}

@@

\subsection{Toy example setup}\label{toy-example-setup}

@@

Any set of concepts representing population, opportunities, and their
associated travel behaviour, whether representing the entire region
uniformly (as will be demonstrated) or representing specific subgroups,
can be substituted into our simple toy example. The purpose of the
following simple example is to demonstrate the calculation and
interpretation of the four accessibility measure variants.

\subsection{Unconstrained
accessibility}\label{unconstrained-accessibility}

@@

For example, Table~\ref{tbl-simple-example-unconstrained-accessibility}
shows \(V^0_{i}\) under each decay function. Comparing across decay
types is meaningless in absolute terms. For instance, the difference in
zone 1 (edge of urban core)'s accessibility under \(f_3\) vs \(f_1\) is
370.92, but in what units? These two values are a product of different
impedance functions ( \emph{physicians-minute\(^{-3}\)} and
\emph{physicians-minute\(^{-0.1}\)}), making the comparison
uninterpretable (and arguably incorrect). The fundamental
uninterpretability of what is an
\emph{opportunity-weighted-travel-impedance} unit remains.

@@

\subsection{Total constrained
accessibility}\label{total-constrained-accessibility}

@@

\subsubsection{Total constrained accessible opportunities: Hansen's
accessibility with a total
constraint}\label{total-constrained-accessible-opportunities-hansens-accessibility-with-a-total-constraint}

@@

\subsubsection{Total constrained accessible population: Reilly's
potential trade territories with a total
constraint}\label{total-constrained-accessible-population-reillys-potential-trade-territories-with-a-total-constraint}

@@

\subsection{Singly constrained
accessibility}\label{singly-constrained-accessibility}

@@

\subsubsection{Singly constrained accessible opportunities: spatial
availability}\label{singly-constrained-accessible-opportunities-spatial-availability}

@@

\subsubsection{Singly constrained accessible population: market
availability}\label{singly-constrained-accessible-population-market-availability}

@@

\subsection{Doubly constrained
accessibility}\label{doubly-constrained-accessibility}

@@

By contrast, the doubly constrained model assumes both the demand
(population) and the supply (opportunity) are known and bounded, and
allocates flows accordingly. This makes it less suitable for traditional
accessibility analysis; namely because origin and destination masses
often differ in kind and units. For instance, the number of people
accessing an opportunity such as park may be known, but the capacity of
each park is not. A doubly constrained approach may make conceptual
sense if the ``potential'' should be contained only in the flows
themselves, meaning the units of population and opportunities are
comparable, have a one-to-one correspondence or are otherwise paired
(e.g., job per worker, student per school-seat, or vaccine doses per
person).

As mentioned, doubly constrained approach to accessibility adopts the
structure of the production-attraction spatial interaction model, where
both population and opportunity totals are fixed. Mathematically, this
model requires the simultaneous imposition of both the population- and
opportunity- constraints in the preceding singly constrained variants
(Eq~\ref{eq-opportunity-constraint} and
Eq~\ref{eq-population-constraint}), namely the sum of population in all
origins should match the sum of opportunities in all destinations
(Eq~\ref{eq-opportunity-population-equality-2}):

@@

This adjustment to the example is summarised in
\textbf{?@tbl-small-system-land-use-doubly-constrained-case}. With the
population (in units of 10,000s of people seeking physicians) and the
opportunities (in units of 10,000s of physician-capacity) per zone. For
the population, we leave this unchanged numerically but we now must keep
in mind that each person interacts with one physician capacity. The
number of providers per destination is however revised to represent
physician capacity, scaled approximately from the original number of
physicians used in previous cases
(Table~\ref{tbl-small-system-land-use}). The system-wide PPR is now 1
(recall: the unmodified example's system PPR is 24.5).

@@

::: \{\#tbl-small-system-land-use-doubly constrained-case .cell
tbl-cap=`Modified simple system with three zones reflecting matched
population and opportunities. Population is in 10,000 persons and
opportunities in 10,000 of physician-capacity.'\} :::
\{.cell-output-display\}

\begin{table}
\fontsize{7.5pt}{9.0pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}rcc}
\toprule
ID (i or j) & Population & Opportunities \\ 
\midrule\addlinespace[2.5pt]
1 & 4 & 7 \\ 
2 & 10 & 5 \\ 
3 & 6 & 8 \\ 
\bottomrule
\end{tabular*}
\end{table}

::: :::

@@

As shown in
Table~\ref{tbl-adjusted-small-system-land-use-doubly-constrained-case-f1cij-access-values}
for the highest-decay scenario \(f_1(c_{ij})\), accessibility is no
longer meaningfully represented as zonal summaries like \(V^D_i\) or
\(M^D_j\), since these values reproduce the original constraints --
i.e., \(V^D_i = O_i\) so the physician-capacity accessible for Zones 1,
2, and 3 would be 4.002, 9.996, and 6.002. Hence, the usefulness of the
doubly constrained measure lies in the interpretation as \(V_{ij}^D\)
values. \(V^D_{ij}\) values represent the number of opportunities from
zone \(j\) allocated to populations in zone \(i\), shaped by both mass
and travel impedance.

To illustrate this, consider the results for Zone 2 (recall: a suburban
zone -- a high-population, low-opportunity, relatively remote). As shown
in
Table~\ref{tbl-adjusted-small-system-land-use-doubly-constrained-case-allfs-access-values-for-zone2},
its intrazonal flow (i.e., \(V^D_{22}\)) declines as travel impedance
decay decreases -- from 4.959 under \(f_1(c_{ij})\) to 2.667 under
\(f_3(c_{ij})\), out of the \textasciitilde10 opportunities allocated to
Zone 2 (a population of 10).

@@

Recall, accessibility is conventionally presented as a zonal value not a
flow. However, in the doubly constrained case, since we force the
allocation of zonal population demand and zonal opportunities supplied
to be paired and allocation to be proportional, \(V_i^D\) is simply the
number of opportunities that matches our known population at \(i\). So
following the logic of the family of accessibility measures, in the
doubly constrained case, \(V_{ij}^D\) flows are the only relevant unit
of analysis: spatial proportional allocations between population and
opportunity capacity. Furthermore, \(V^D_{ij}\) and its transposed
counterpart \(M^D_{ji}\) are structurally identical, differing only in
interpretation (referring to \(\kappa_{ij}^D\) and
\(\hat \kappa_{ij}^D\)): one reflects the proportional allocation of
opportunity to population flows; the other, population to opportunity
flows.

@@

And as mentioned, these units are often misaligned -- for instance, we
may not know how much park space, grocery area, or childcare capacity is
accessible per person. When they do align -- such as people to physician
capacity -- we are modeling realised access flows based on known
quantities of \emph{those that interact} and the \emph{interacted}. In
such cases, the traditional accessibility question can be seen to be
already answered by the known information (i.e., how many opportunities
can be reached by a zone? Answer: the number of people at that zone).
For this reason, we do not foresee the doubly constrained measure being
widely used in accessibility analysis as the literature has largely
focused on questions of `potential' access, not on predicting flows of
realised access.

\section{Conclusions}\label{conclusions}

@@

Lastly, the doubly constrained case is introduced. In this case, the
sums must equal both the regional total and ensure that no zone
allocates more opportunities than it has available. Specifically,
accessibility values for each \(i\)-\(j\) pair must be a proportion of
the zonal opportunity and population values simultaneously. For example,
the accessibility at Zone 1 must equal the sum of opportunities from
zones 1, 2, and 3, as well as the sum of the population at Zone 1.
Satisfying the double constraint means the opportunities and population
data must match one-to-one, so working with the accessibility
\(i\)-\(j\) pair values should be of interest. In this sense, the
research question should be concerned with `access' (how many
opportunities accessed from \(j\) at \(i\) based on given zonal
opportunities and populations) instead of potential spatial interaction
(e.g., typically expressed as a zonal summary measure of how many
opportunities one could reach out of a regional total and/or
zonal-allocation).

Overall, and building on Wilson's \citep{wilson1971} foundational work,
this paper proposes a unified framework for analyzing gravity-based
accessibility. By reintroducing Wilson's proportionality constants, the
family of constrained accessibility measures restores measurement units
to accessibility estimates. This enhancement provides a more
interpretable, consistent, and theoretically grounded basis for
accessibility analysis, which could help advance the adoption of
accessibility-oriented planning.

That said, there have been more recent developments in the accessibility
literature, including novel person-based approaches that are
time-sensitive \citep{yang2024evaluating, braga2023evaluating},
behavioural \citep{kar2024inclusive, lu2014effects} or utility-based
\citep{guzman2023much, ben1985discrete}, that are not based on top-down
approaches such as Wilson's model formalized through the
entropy-maximisation procedure. While gravity-based measures of
accessibility dominate the applied literature, future work could further
explore how these ideas of proportionality constants and balanced units
could also help inform these and other new modeling approaches.

>>>>

\linenumbers
\section{1. Introduction}\label{introduction}

@@

This paper makes two contributions. First, we review how spatial
interaction modeling and accessibility share similar origins but have
diverged in focus and interpretation. Second, we introduce a family of
accessibility measures grounded in spatial interaction principles,
including total, singly, and doubly constrained cases and variants of
``accessible opportunities'' and ``accessible population''. These cases
and variants align with common measures such as Hansen-type
accessibility \citep{hansen1959}, competitive accessibility measures
such as the 2SFCA method \citep{shen1998, luo2003}, and market potential
models
\citep{harris_market_1954, vickermanAccessibilityAttractionPotential1974}.

@@

The remainder of this paper proceeds as follows. Sections 2 through 4
trace the historical development of spatial interaction and
accessibility research, beginning with Newtonian gravitational analogies
and Carey (1858) \citep{careyPrinciplesSocialScience1858} (Section 2),
moving through early researchers like Ravenstein (1885)
\citep{ravensteinLawsMigration1885} to Stewart (1948)
\citep{stewartDemographicGravitationEvidence1948} who theorised and
formalized spatial interaction patterns (Section 3), and examining how
the ``gravity-based'' accessibility approach in Hansen (1959)
\citep{hansen1959} became the dominant approach in planning practice
(Section 4). Section 5 presents the entropy-based family of spatial
interaction models in Wilson (1971) \citep{wilson1971}, explaining how
the introduction of ``constraints'' (based on top-down known information
as part of entropy-maximisation) produce interpretable, unit-consistent
flow estimates. Section 6 explores why accessibility and spatial
interaction literature diverged into separate branches despite their
shared conceptual foundations. Section 7 constitutes the paper's core
contribution: we derive a family of accessibility measures corresponding
to different constraints applied -- unconstrained, singly constrained,
and doubly constrained cases -- demonstrating how each yields zone-level
accessibility values expressed in meaningful units (opportunities or
population) rather than unit-inconsistent indices. We illustrate each
measure with numerical examples that clarify the practical implications
of different constraint assumptions. Section 8 concludes by discussing
how these constrained measures can inform planning decisions and improve
clarity in accessibility analysis.

@@

\section{2. Newtonian's roots of human spatial interaction
research}\label{newtonians-roots-of-human-spatial-interaction-research}

@@

\section{3. Early research on human spatial interaction: from Ravenstein
(1885) to Stewart
(1948)}\label{early-research-on-human-spatial-interaction-from-ravenstein-1885-to-stewart-1948}

@@

\section{4. Hansen's gravity-based accessibility to
today}\label{grav-to-today}

@@

\section{5. Wilson's family of spatial interaction
models}\label{wilsons-family-of-spatial-interaction-models}

@@

Wilson's work is notable for many reasons. Rather than relying on a
universal constant like \(G\) or a scaling factor to balance units,
Wilson's models calibrate interaction flows through known empirical
constraints using principles of entropy maximisation. This results in
interpretable, balanced (given the system knowns are expressed in the
constraints), and unit-consistent \(ij\) flows. The balancing factors
themselves have been subject to various interpretations -- as terminal
costs \citep{dieter1962distribution}, weighted mean values
\citep{kirbyNormalizingFactorsGravity1970}, or as accessibility measures
themselves \citep{cesario1977new} (as suggested in Wilson
\citep{wilson1971}) and as rents
\citep{morphetGravityModelCalibration2023} -- reflecting ongoing efforts
to understand what these mathematical constructs represent
behaviourally. In this way, the spatial interaction modeling tradition
can be seen to have succeeded where accessibility modeling stalled.
While Wilson's model produces results that are in units of flow tethered
to the system of analysis, which facilitates such interpretations,
Hansen-type measures (still widely used today in accessibility work)
yield outputs that reflect proportional -- not equal -- relationships
and typically lack interpretable units.

@@

\section{6. Accessibility and spatial interaction modelling: two
divergent research
streams}\label{accessibility-and-spatial-interaction-modelling-two-divergent-research-streams}

@@

\section{7. A family of accessibility measures: from proportionality to
equality}\label{a-family-of-accessibility-measures-from-proportionality-to-equality}

@@

\subsection{7.1. Toy example setup}\label{toy-example-setup}

@@

Any set of concepts representing population, opportunities, and their
associated travel behaviour, whether representing the entire region
uniformly (as will be demonstrated) or representing specific subgroups,
can be substituted into our simple toy example. The purpose of the
following simple example is to demonstrate the calculation and
interpretation of the four accessibility measure variants. As well, the
family of measures proposed will be available in the
\href{https://ipeagit.github.io/accessibility/}{\{accessibility\} R
package} for convenient use in future studies.

\subsection{7.2. Unconstrained
accessibility}\label{unconstrained-accessibility}

@@

For example, Table~\ref{tbl-simple-example-unconstrained-accessibility}
shows \(V^0_{i}\) under each decay function. Comparing across decay
types is meaningless in absolute terms. For instance, the difference in
zone 1 (edge of urban core)'s accessibility under \(f_3\) vs \(f_1\) is
370.92, but in what units? These two values are a product of different
impedance functions \emph{physicians-minute\(^{-0.1}\)} and
\emph{physicians-minute\(^{-3}\)}), making the direct comparison
uninterpretable (and arguably incorrect). The fundamental
uninterpretability of what is an
\emph{opportunity-weighted-travel-impedance} unit remains.

@@

\subsection{7.3. Total constrained
accessibility}\label{total-constrained-accessibility}

@@

\subsubsection{7.3.1. Total constrained accessible opportunities:
Hansen's accessibility with a total
constraint}\label{total-constrained-accessible-opportunities-hansens-accessibility-with-a-total-constraint}

@@

\subsubsection{7.3.2. Total constrained accessible population: Reilly's
potential trade territories with a total
constraint}\label{total-constrained-accessible-population-reillys-potential-trade-territories-with-a-total-constraint}

@@

\subsection{7.4. Singly constrained
accessibility}\label{singly-constrained-accessibility}

@@

\subsubsection{7.4.1. Singly constrained accessible opportunities:
spatial
availability}\label{singly-constrained-accessible-opportunities-spatial-availability}

@@

\subsubsection{7.4.2. Singly constrained accessible population: market
availability}\label{singly-constrained-accessible-population-market-availability}

@@

\subsection{7.5. Doubly constrained
accessibility}\label{doubly-constrained-accessibility}

@@

By contrast, the doubly constrained model assumes both the demand
(population) and the supply (opportunity) are known and bounded, and
allocates flows accordingly. This makes it less suitable for traditional
accessibility analysis; namely because origin and destination masses
often differ in kind and units. For instance, the number of people
accessing an opportunity such as park may be known, but the capacity of
each park is not. A doubly constrained approach may make conceptual
sense if the ``potential'' should be contained only in the flows
themselves, meaning the units of population and opportunities are
comparable, have a one-to-one correspondence or are otherwise paired
(e.g., job per worker, student per school-seat, or vaccine doses per
person). Mathematically, this model requires the simultaneous imposition
of both the population- and opportunity- constraints in the preceding
singly constrained variants (Eq~\ref{eq-opportunity-constraint} and
Eq~\ref{eq-population-constraint}), namely the sum of population in all
origins should match the sum of opportunities in all destinations
(Eq~\ref{eq-opportunity-population-equality-2}):

@@

This adjustment to the example is summarised in
Table~\ref{tbl-small-system-land-use-doubly-constrained-case}. With the
population (in units of 10,000s of people seeking physicians) and the
opportunities (in units of 10,000s of physician-capacity) per zone. For
the population, we leave this unchanged numerically but we now must keep
in mind that each person interacts with one physician capacity. The
number of providers per destination is however revised to represent
physician capacity, scaled approximately from the original number of
physicians used in previous cases
(Table~\ref{tbl-small-system-land-use}). The system-wide PPR is now 1
(recall: the unmodified example's system PPR is 24.5).

@@

\caption{\label{tbl-small-system-land-use-doubly-constrained-case}Modified
simple system with three zones reflecting matched population and
opportunities. Population is in 10,000 persons and opportunities in
10,000 of physician-capacity.}

\fontsize{7.5pt}{9.0pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}rcc}
\toprule
ID (i or j) & Population & Opportunities \\ 
\midrule\addlinespace[2.5pt]
1 & 4 & 7 \\ 
2 & 10 & 5 \\ 
3 & 6 & 8 \\ 
\bottomrule
\end{tabular*}

@@

As shown in
Table~\ref{tbl-adjusted-small-system-land-use-doubly-constrained-case-f1cij-access-values}
for the highest-decay scenario \(f_1(c_{ij})\), accessibility is no
longer meaningfully represented as zonal summaries like \(V^D_i\) or
\(M^D_j\), since these values reproduce the original constraints i.e.,
\(V^D_i = O_i\) hence the physician-capacity accessible for Zones 1, 2,
and 3 are 4.002, 9.996, and 6.002. The usefulness of the doubly
constrained measure lies in the interpretation as \(V_{ij}^D\) values;
the number of opportunities from zone \(j\) allocated to populations in
zone \(i\) shaped by both mass and travel impedance.

To illustrate this concept, consider the results for Zone 2 (recall: a
suburban type zone, with a higher population, lower amount of
opportunities, and relatively remote). As shown in
Table~\ref{tbl-adjusted-small-system-land-use-doubly-constrained-case-allfs-access-values-for-zone2},
its intrazonal flow (i.e., \(V^D_{22}\)) declines as travel impedance
decay decreases -- from 4.959 under \(f_1(c_{ij})\) to 2.667 under
\(f_3(c_{ij})\), out of the \textasciitilde10 opportunities allocated to
Zone 2 (a population of 10).

@@

Accessibility is conventionally presented as a zonal value not a flow.
However, in the doubly constrained case, since we force the allocation
of zonal population demand and zonal opportunities supplied to be paired
and allocation to be proportional, \(V_i^D\) is simply the number of
opportunities that matches our known population at \(i\). Following the
logic of the family of accessibility measures, in the doubly constrained
case, \(V_{ij}^D\) flows are the only relevant unit of analysis: spatial
proportional allocations between population and opportunity capacity.
Furthermore, \(V^D_{ij}\) and its transposed counterpart \(M^D_{ji}\)
are structurally identical, differing only in interpretation (referring
to \(\kappa_{ij}^D\) and \(\hat \kappa_{ij}^D\)): one reflects the
proportional allocation of opportunity to population flows; the other,
population to opportunity flows.

@@

And as mentioned, these units are often misaligned. For instance, we may
not know how much park space, grocery area, or childcare capacity is
accessible per person. When they do align, such as people to physician
capacity, we would be modeling realised access flows based on known
quantities of \emph{those that interact} and the \emph{interacted}. In
such cases, the traditional accessibility question can be seen to be
already answered by the known information (i.e., how many opportunities
can be reached by a zone? Answer: the number of people at that zone).
For this reason, we do not foresee the doubly constrained measure being
widely used in accessibility analysis as the literature has largely
focused on questions of `potential' not on predicting flows of realised
access.

\section{8. Conclusions}\label{conclusions}

@@

Lastly, the doubly constrained case is introduced. In this case, the
sums must equal both the regional total and ensure that no zone
allocates more opportunities than it has available. Specifically,
accessibility values for each \(i\)-\(j\) pair must be a proportion of
the zonal opportunity and population values simultaneously. For example,
the accessibility at Zone 1 must equal the sum of opportunities from
Zones 1, 2, and 3, as well as the sum of the population at Zone 1.
Satisfying the double constraint means the opportunities and population
data must match one-to-one, so working with the accessibility
\(i\)-\(j\) pair value should be of research interest.

Building on Wilson's \citep{wilson1971} foundational work, this paper
proposes a unified framework for analyzing gravity-based accessibility.
By reintroducing Wilson's proportionality constants, the family of
constrained accessibility measures restores measurement units to
accessibility estimates. This enhancement provides a more interpretable,
consistent, and theoretically grounded basis for accessibility analysis,
which could help advance the adoption of accessibility-oriented
planning.

While this work exclusively focused on top-down gravity-based
accessibility measures, there have been recent developments in the
accessibility literature that include person-based approaches that are
time-sensitive \citep{yang2024evaluating, braga2023evaluating},
behavioural \citep{kar2024inclusive, lu2014effects} or utility-based
\citep{guzman2023much, ben1985discrete}. While gravity-based measures of
accessibility still dominate the applied literature, future work could
further explore how these ideas of proportionality constants and
balanced units could also help inform these and other new modeling
approaches.
